
\documentclass{tccv}
\usepackage[english]{babel}
\newcommand{\at}{\makeatletter @\makeatother}

\begin{document}

\part{Sayan Das}

\section{Work Experience}

\begin{yearlist}
	
	\item{present}
	{Quinbay Technologies Sr. SDE (1 year - present) (\href{https://quinbay.com}{quinbay.com})}
	{
		Worked for \href{blibli.com}{BliBli.com}, in optimising search infrastructure in term of cost and latency. \newline
		Planned, benchmarked and planned migration strategy to move from GCP N1 (Intel 1st) to N2D (AMD EPYC) instance, to gain \textbf{~30\% gain in single core performance}
		\newline
		Strategized, developed and benchmark multi-sharded solr collection from single shard to better scale the cluster horizontally  with growing index size, making the collection \textbf{future proof in terms of hardware resources for next 5years}
	}
	
	\item{2018}
	{Coviam Technologies SDE (2 years 4 months) (\href{https://coviam.com}{coviam.com})}
	{
		Worked on developing low latency distributed system which can search over millions of documents \newline
		Researched and developed upon scaling up Apache Solr to support \textbf{10x more document} without compromising upon the performance by re-architecting search infrastructure.
		\newline
		Tuned garbage collector for solr cluster, to  \textbf{reduce 90\% of compute workload} done by garbage collector. Here is the \hyperlink{https://medium.com/bliblidotcom-techblog/optimizing-solr-resources-with-g1-448bb9c49d46}{article} published for the entire setup and process.
	}
	
	\item{2017}
	{Coviam Technologies Intern (6 months) (\href{https://coviam.com}{coviam.com})}
	{
		Understanding and learning the core frameworks and technologies used as a standard. \newline
		Designed and developed the entire adword feed generation system  which include Google, Facebook and other affiliated partners \newline
		Deep diving through how search works in an e-commerce world \newline
	}
	
	\item{2016}
	{Signzy Technologies Pvt Ltd Intern (2 months) (\href{https://signzy.com}{signzy.com})}
	{Core API integrations to user facing product. Sandbox system for API docs for the clients.}
	
\end{yearlist}

\section{Honors and Awards}

\begin{eventlist}
	
	\item{October 2021}
	{High Impact Award, Quinbay Tech.}
	{}
	
	
	
	\item{September 2021}
	{SPOT Award, Quinbay Tech.}
	{}
	
	\item{September 2018}
	{Best New Hire Award, Coviam Tech.}
	{}
	
	
\end{eventlist}

\personal
[]
{302, 31/4/1 - Charvik Enclave, Somasundarpalya, HSR Layout, Bangalore}
{+91 9176046531}
{sayan.das\at quinbay.com}

\section{Education}

\begin{yearlist}
	
	\item[Class XII: 88\% (CBSE Board)]{2000 -- 2014}
	{High School}
	{Delhi Public School, Haridwar}
	
	\item[CGPA: 8.48]{2014 -- 2018}
	{B.Tech in Computer Science \& Eng.}
	{SRM University, Kattankulathur}
	
\end{yearlist}


\section{Communication skills}

\begin{factlist}
	\item{Hindi}{Native speaker}
	\item{English}{Oral: fair -- Written: good}
	\item{Bengali}{Oral: good}
\end{factlist}

\section{Software skills}

\begin{factlist}
	
	\item{Good level}
	{Java 8, Python 2.7, Spring Boot, Solr }
	
	\item{Intermediate}
	{Bash, Mongo, Redis, Vue.js, Angular 1.x}
	
	\item{Basic level}
	{\LaTeX, SQL Databases}
	
\end{factlist}

\section{Social Links}

\begin{factlist}
	
	\item{GitHub}
	{\href{https://github.com/poke19962008}{github.com/poke19962008}}
	\item{Stack Overflow}
	{\href{https://stackoverflow.com/users/1600172}{stackoverflow.com/users/1600172}}
	\item{Linked In}
	{\href{https://www.linkedin.com/in/sayan-das-63a71b7b/}{linkedin.com/in/sayan-das-63a71b7b/}}
	\item{Word Press}
	{\href{https://poke19962008.wordpress.com}{poke19962008.wordpress.com}}
	\item{Code Chef}
	{\href{https://www.codechef.com/users/poke19962008}{codechef.com/users/poke19962008}}
	\item{Twitter}
	{\href{https://twitter.com/iSayan16}{@iSayan16}}
	     
	
\end{factlist}

\end{document}